---
title: "Overview & Background"
subtitle: "Data Visualization and Analysis in the Era of COVID-19"
author: "Damian Betebenner, Adam VanIwaarden & Nathan Dadey"
institute: "Center for Assessment"
date: "February 18th, 2022 (updated: `r toOrdinal::toOrdinalDate(Sys.Date())`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      titleSlideClass: ["center", "middle", "my-title"]

---
class: inverse, center, middle

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

```{r style-share-again, echo=FALSE}
xaringanExtra::style_share_again(
  share_buttons = c("twitter"),
  background = "#009C49",
  foreground = "#FFFFFF"
)
```

```{r xaringan-logo, echo=FALSE}
xaringanExtra::use_logo(
  image_url = "https://centerforassessment.github.io/assets/favicon.png",
  width = "55px",
  height = "64px",
  position = xaringanExtra::css_position(top = "0.5em", right = "0.5em"),
  link_url = "https://www.nciea.org"
)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```

```{r xaringanExtra-clipboard, echo=FALSE}
xaringanExtra::use_clipboard()
```

# Overview

---

# Welcome to our NCME 2022
# Training Session

--

## The Presenters

- [Damian Betebenner](https://github.com/dbetebenner), Center for Assessment

--

- [Adam VanIwaarden](https://github.com/adamviAdam), Center for Assessment

--

- [Nathan Dadey](https://github.com/ndadey), Center for Assessment


---

# Data Visualization and Analysis in the Era of COVID-19

--

## The Agenda: Day 1

- Overview and Background: April 10th, 1:00 to 2:00 pm [@dbetebenner](https://github.com/dbetebenner)

--

- Computer Setup: April 10, 2:00 to 2:30

--

- Break: April 10, 2:30 to 2:45

--

- Academic Impact (Part 1): April 10, 2:45 to 3:45 pm [@dbetebenner](https://github.com/dbetebenner)

--

- Missing Data (Part 1): April 10, 3:45 to 4:45 pm [@ndadey](https://github.com/ndadey)

--

- Summary and next steps: April 10, 4:45 to 5:00 pm [@dbetebenner](https://github.com/dbetebenner)

---

# Data Visualization and Analysis in the Era of COVID-19

--

## The Agenda: Day 2

- Missing Data (Part 2): April 11, 1 to 3:00 pm [@adamvi](https://github.com/adamviAdam)

--

- Break: April 11, 3:00 to 3:15

--

- Academic Impact (Part 2): April 11, 3:15 to 4:45 pm [@dbetebenner](https://github.com/dbetebenner)

--

- Wrap-up/Q&A: April 11, 4:45 to 5:00 pm


---

# Data Visualization and Analysis in the Era of COVID-19

--

## Resources
--

All presentations and materials associated with the training session are located in a GitHub repo:

https://github.com/centerforassessment/NCME_2022_Training_Session

--

Associated with the repo is a GitHub hosted website and contains all the presentations and associated documentation

https://centerforassessment.github.io/NCME_2022_Training_Session/

--

If you're interested in learning how to use GitHub in this way please join our NCME 2022 Demonstration Session:

Using GitHub for Open-Source Analytics, Reporting, and Dissemination of Research. Saturday April 23rd, 1:15 to 2:45 PT.


---
class: inverse, center, middle

# Background

---

# COVID-19 Academic Impact

--

### The pandemic and all the ensuing disruptions functioned/functions as an “academic headwind”, impeding (in general) the academic progress of students.

--

### Academic Impact implies a counterfactual: Where would the student (or system) have been had the pandemic not occurred?

--

- Analyses necessarily utilize the performance of a pre-pandemic, cohort (presumably comparable to the current cohort) to compare.
- Note that without pre-pandemic data on students, it is impossible to entertain questions of what academic impact has occurred.


---

# COVID-19 Academic Impact

### Headwinds impede progress in two ways:

--

1. They slow one’s rate of progress (speedometer)
2. And by slowing one’s rate of progress they lead to less distance being travelled (odometer).

--

### In education these two impediments manifest as:

--

1. Decrease in student growth.
2. Decrease in student attainment.

---

# COVID-19 Academic Impact

### The impact to student attainment and student growth frame the two primary types of analyses that will be discussed in this training session

1. Academic Impact as it relates to change (i.e. decrease) in student attainment
2. Academic Impact as it relates to change (i.e., decrease) in student growth

--

### Status based analyses of academic impact will be discussed first. Growth based analyses of academic impact will be discussed second.

---

class: center, bottom

```{r echo=FALSE}
magick::image_read_pdf("Figures/Academic_Impact_ELA_Grade_5.pdf")
```

---

class: center, bottom

```{r echo=FALSE}
magick::image_read_pdf("Figures/Academic_Impact_Mathematics_Grade_5.pdf")
```

---

class: center, bottom

```{r echo=FALSE}
magick::image_read_pdf("Figures/Academic_Impact_Overview_Overall_COMPILATION_Hybrid_ANONYMIZED.pdf")
```

---

class: center, bottom

```{r echo=FALSE}
magick::image_read_pdf("Figures/Academic_Impact_Overview_Quintile_1_COMPILATION_Hybrid_ANONYMIZED.pdf")
```
